Figures

### 2018-12-14 figures/02_hierarchical_demo.Rmd
use lagosnegis not lagosextra

```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
library(dplyr)
library(LAGOSextra)
library(sf)
library(ggplot2)
library(cowplot)
library(classInt)

@@

hu4 <-  LAGOSextra::query_gis("HU4", "ZoneID", ids$hu4_zoneid) %>%
  st_cast(to = "MULTIPOLYGON") %>%
  left_join(ids, by = c("ZoneID" = "hu4_zoneid"))

>>>>

```{r hu4_n, echo=FALSE, message=TRUE, eval=TRUE}
library(dplyr)
library(LAGOSNEgis)
library(sf)
library(ggplot2)
library(cowplot)
library(classInt)

@@

hu4 <-  LAGOSNEgis::query_gis("HU4", "ZoneID", ids$hu4_zoneid) %>%
  st_cast(to = "MULTIPOLYGON") %>%
  left_join(ids, by = c("ZoneID" = "hu4_zoneid"))

### 2018-12-14 figures/06_lulc_buffer_demo.Rmd
use lagosnegis not lagosextra

```{r 06_lulc_buffer_demo, echo=FALSE, eval=TRUE}
# setwd("figures")
library(nhdR)
library(LAGOSextra)
library(mapview)
library(FedData)
library(dplyr)
library(ggplot2)
library(raster)
library(sf)
library(cowplot)

>>>>

```{r 06_lulc_buffer_demo, echo=FALSE, eval=TRUE}
# setwd("figures")
library(nhdR)
library(LAGOSNEgis)
library(mapview)
library(FedData)
library(dplyr)
library(ggplot2)
library(raster)
library(sf)
library(cowplot)
